Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-26 paper.qmd
Updated Figure 17

distance_df_small_edges_mnist <- distance_mnist |>
  filter(distance < benchmark_mnist) |>
  filter(!(row_number() %in% c(143, 144, 162)))

tr_from_to_df_mnist <- inner_join(
  tr_from_to_df_mnist, distance_df_small_edges_mnist, 
  by = c("from", "to"))

@@

free(trimesh_removed_mnist) + mnist_proj_tsne_model1 +
  mnist_proj_tsne_model2 + mnist_proj_tsne_model3 +
  plot_layout(ncol = 2)
```

>>>>

distance_df_small_edges_mnist <- distance_mnist |>
  filter(distance < benchmark_mnist) |>
  filter(!(row_number() %in% c(155, 554, 140)))

tr_from_to_df_mnist <- inner_join(
  tr_from_to_df_mnist, distance_df_small_edges_mnist, 
  by = c("from", "to")) |>
  mutate(ID = row_number())

@@

free(trimesh_removed_mnist) + mnist_proj_tsne_model1 +
  mnist_proj_tsne_model2 + mnist_proj_tsne_model3 +
  plot_layout(ncol = 2)
